\newpage

\centering \Large \textbf{PUBLICATION LIST}
\normalsize

\begin{rSection}{Patents}
\begin{enumerate}
\itemsep-0.5em

\item Chuprov, S., \& Reznik, L. ``Federated Learning with A Compromised Unit Exclusion from Receiving Global Model Updates''.\\
\scriptsize \textit{Provisional application filed on January 13, 2023}\normalsize

\item Chuprov, S., \& Reznik, L. ``Network Adjustment based on Machine Learning End System Performance Monitoring Feedback''.\\
\scriptsize\textit{Provisional application filed on September 14, 2022}\normalsize

\end{enumerate}
\end{rSection}

\begin{rSection}{Refereed Journal Publications}
\begin{enumerate}
\itemsep-0.5em

\item Berezovskaya, O., Chuprov, S., Neverov, E., \& Sadreev, E. (2023). ``Review and Comparison of Lightweight Modifications of the AES Cipher for a Network of Low-Power Devices'' in Automatic Control and Computer Sciences. 2022, no. 56, pp. 994-1006. doi: 10.3103/S0146411622080028. \href{https://link.springer.com/article/10.3103/S0146411622080028}{\nolinkurl{URL}}

\item Melnikov, T., Chuprov, S., Lazarev, E., Gataullin, R., \& Viksnin, I. (2022). ``Improving Reputation and Trust-Based Approach with Reliability Indicators for Autonomous Vehicles Intergroup Communication'' in Tomsk State University Journal of Control and Computer Science. 2022, no. 61, pp. 108-117.
\href{http://journals.tsu.ru/informatics/en/&journal_page=archive&id=2302#:~:text=Improving%20reputation%20and,vehicles%20intergroup%20communication}{\nolinkurl{URL}}

\item Marinenkov, E., Chuprov, S., Tursukov, N., Kim, I., \& Viksnin, I. (2022). ``Study on Destructive Informational Impact in Unmanned Aerial Vehicles Intergroup Communication'' in Symmetry. 2022. Vol. 14, no. 8, pp. 1-18. \href{https://www.mdpi.com/2073-8994/14/8/1580/htm}{\nolinkurl{URL}} \scriptsize{\textcolor{red}{\textit{Published in Special Issue}}}\normalsize

\item Buzina, E., Chuprov, S., Tursukov, N., Belyaev, P., \& Viksnin, I. (2022). ``Algorithm for Uniform Coverage of the Monitoring Territory by Unmanned Aerial Vehicles'' in LETI Transactions on Electrical Engineering \& Computer Science. 2022. Vol. 15, no. 5/6. P. 41–50. doi: 10.32603/2071-8985-2022-15-5/6-41-50. -- \textit{in Russian.} \href{https://izv.etu.ru/ru/arhive/2022/5-6/41-50}{\nolinkurl{URL}}

\item Berezovskaya, O., Chuprov, S., Neverov, E., \& Sadreev., E. (2022). ``Review and Comparison of AES Lightweight Modifications for a Low-Power Devices Network'' in Problems of Information Security. Computer Systems. no. 2, pp. 35-50. doi: 10.48612/jisp/gp9v‑96dh‑32\\
v1. -- \textit{in Russian.} \href{https://jisp.ru/article/obzor-i-sravnenie-legkovesnyh-modifikatsij-shifra-aes-dlya-seti-malomoshhnyh-ustrojstv/}{\nolinkurl{URL}}

\item Viksnin, I., Marinenkov, E., \& Chuprov, S. (2022). ``A Game Theory approach for communication security and safety assurance in cyber-physical systems with Reputation and Trust-based mechanisms'' in Scientific and Technical Journal of Information Technologies, Mechanics and Optics, vol. 22, no. 1, pp. 47–59. doi: 10.17586/2226-1494-2022-22-1-47-59. \href{https://ntv.ifmo.ru/en/article/20971/primenenie_teorii_igr_dlya_obespecheniya_bezopasnosti_kommunikacii_kiberfizicheskoy_sistemy_s_ispolzovaniem_mehanizmov_reputacii_i_doveriya.htm}{\nolinkurl{URL}}

\item Chuprov, S., Gataullin, R., \& Viksnin, I. (2021). ``Vulnerabilities Assesment in Mobile Robotic Control System'' in Proceedings of the St. Petersburg State Electrotechnical University LETI, vol. 10, pp. 70-75. -- \textit{in Russian}. \href{https://izv.etu.ru/ru/arhive/2021/10/70-75}{\nolinkurl{URL}}

\item Khokhlov, I., Reznik, L., \& Chuprov, S. (2020). ``Framework for Integral Data Quality and Security Evaluation in Smartphones'' in IEEE Systems Journal, vol. 15, no. 2, pp. 2058-2065, doi: 10.1109/JSYST.2020.2985343. \href{https://ieeexplore.ieee.org/abstract/document/9080556}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., Tursukov, N., \& Nedosekin, G. (2020). Empirical Study on Discrete Modeling of Urban Intersection Management System. International Journal of Embedded and Real-Time Communication Systems (IJERTCS), vol. 11(2), pp. 16-38, doi: 10.4018/IJERTCS.2020040102. \href{https://www.igi-global.com/article/empirical-study-on-discrete-modeling-of-urban-intersection-management-system/258082}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., Marinenkov, E., Usova, M., Lazarev, E., Melnikov, T., \& Zakoldaev, D. (2019). Reputation and Trust Approach for Security and Safety Assurance in Intersection Management System. Energies, 12(23), 4527, doi: 10.3390/en12234527. \href{https://www.mdpi.com/1996-1073/12/23/4527}{\nolinkurl{URL}}
\end{enumerate}

\end{rSection}

\begin{rSection}{Refereed Conferences' Proceedings and presentations}
\begin{enumerate}
\itemsep-0.5em

\item Chuprov, S., Reznik, L., \& Grigoryan, G. (2022). ``Study on Network Importance for ML End Application Robustness'' in 2023 IEEE International Conference on Communications. \\
\scriptsize \textit{Accepted for presentation and publication. Will be published after June 2023.} \normalsize

\item Chuprov, S., Satam, A. N., \& Reznik, L. (2022). ``Are ML Image Classifiers Robust to Medical Image Quality Degradation?'' in 2022 IEEE Western New York Image and Signal Processing Workshop (WNYISPW), 2022, pp. 1-4, doi: 10.1109/WNYISPW57858.2022.9983488.
\href{https://ieeexplore.ieee.org/document/9983488}{\nolinkurl{URL}}

\item Chuprov, S., Khokhlov, I., Reznik, L., \& Manghi, K. (2022). ``Multi-Modal Sensor Selection with Genetic Algorithms'' in 2022 IEEE Sensors, 2022, pp. 1-4, doi: 10.1109/SENSORS52175.2022.9967296.
\href{https://ieeexplore.ieee.org/document/9967296}{\nolinkurl{URL}}

\item Khokhlov, I., Chuprov, S., \& Reznik, L. (2022). ``Integrating Security with Accuracy Evaluation in Sensors Fusion'' in 2022 IEEE Sensors, 2022, pp. 1-4, doi: 10.1109/SENSORS52175.2022.9967235.
\href{https://ieeexplore.ieee.org/document/9967235}{\nolinkurl{URL}}

\item Chuprov, S., Khokhlov, I., Reznik, L., \& Shetty, S. (2022). ``Influence of Transfer Learning on Machine Learning Systems Robustness to Data Quality Degradation'' in 2022 International Joint Conference on Neural Networks (IJCNN 2022), 2022, pp. 1-8, doi: 10.1109/IJCNN55064.2022.9892247. \href{https://ieeexplore.ieee.org/abstract/document/9892247}{\nolinkurl{URL}}

\item Chuprov, S., Reznik, L., Obeid, A., \& Shetty, S. (2022). ``How Degrading Network Conditions Influence Machine Learning End Systems Performance?'' in IEEE INFOCOM 2022 - IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS), 2022, pp. 1-6, doi: 10.1109/INFOCOMWKSHPS54753.2022.9798388. \href{https://ieeexplore.ieee.org/abstract/document/9798388?casa_token=F_FXxDTupigAAAAA:OyMilDynWbzOuAZ4SjcNAbJR9_2PQubP-8I1GWdwoHncOIxMz7boIrtaOs2ik7b6BY_C72m2DQ}{\nolinkurl{URL}}

\item Chuprov, S., Gataullin, R., Neverov, E., Belyaev, P., Kim, I., \& Viksnin, I. (2022). ``Police Office Model Performance and Security Evaluation in a Simulated Group of Mobile Robots'' in The 5th International Conference on Future Networks \& Distributed Systems (ICFNDS 2021). Association for Computing Machinery, New York, NY, USA, pp. 606–615, doi: 10.1145/3508072.3508195. \href{https://dl.acm.org/doi/abs/10.1145/3508072.3508195?casa_token=emU3vhg0J98AAAAA:DwcQ-b1JVuMRRTeGcLDn6ZFtiSzuP4CL88yTMTYZIYGehMFD-kwUEAlGoYH-j-yRxkK1xONmBQo}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., Melnikov, T., Reznik, L., \& Khokhlov, I. (2021). ``Improving Knowledge Based Detection of Soft Attacks Against Autonomous Vehicles with Reputation, Trust and Data Quality Service Models'' in 2021 IEEE International Conference on Smart Data Services (SMDS), pp. 115-120. \href{https://ieeexplore.ieee.org/document/9592379}{\nolinkurl{URL}}

\item Domnitsky, E., Mikhailov, V., Zoloedov, E., Alyukov, D., Chuprov, S., Marinenkov, E., \& Viksnin, I. (2021). ``Software Module for Unmanned Autonomous Vehicle’s On-board Camera Faults Detection and Correction'' in CEUR Workshop Proceedings, Vol. 2893, pp. 1-10. \href{http://ceur-ws.org/Vol-2893/paper_18.pdf}{\nolinkurl{URL}}

\item Lyakhovenko, Y., Viksnin, I., \& Chuprov, S. (2021). ``Integrating Smart Contracts into Smart Factory Elements’ Informational Interaction Model'' in CEUR Workshop Proceedings, Vol. 2893, pp. 1-6. \href{http://ceur-ws.org/Vol-2893/short_4.pdf}{\nolinkurl{URL}}

\item Usova, M., Viksnin, I., \& Chuprov, S. (2021). ``Informational Messages and Space Models Application in Smart Factory Concept'' in CEUR Workshop Proceedings, Vol. 2893, pp. 1-8. \href{http://ceur-ws.org/Vol-2893/short_3.pdf}{\nolinkurl{URL}}

\item Khanh, T.D., Komarov, I., Don, L.D., Iureva, R., \& Chuprov, S. (2020). ``TRA: Effective Authentication Mechanism For Swarms Of Unmanned Aerial Vehicles'' in 2020 IEEE Symposium Series on Computational Intelligence, pp. 1852-1858, doi: 10.1109/SSCI47803.2020.\\
9308140. \href{https://ieeexplore.ieee.org/document/9308140}{\nolinkurl{URL}}

\item Melnikov, T., Lazarev, E., Berezovskaya, O., Chuprov, S., \& Viksnin, I. (2020). ``Empirical Study on Premises Monitoring Algorithm Implementation in Mobile Robotic System'' in The International Conference ``Nonlinearity, Information and Robotics'', pp. 1-6, doi: 10.1109/NIR50484.2020.9290188. \href{https://ieeexplore.ieee.org/document/9290188}{\nolinkurl{URL}}

\item Usova, M., Chuprov, S., \& Viksnin, I. (2020). ``Informational Space and Messages Interaction Models for Smart Factory Concept'' in 2020 IEEE International Workshop on Metrology for Industry 4.0 \& IoT, pp. 617-621, doi: 10.1109/MetroInd4.0IoT48571.2020.9138292. \href{https://ieeexplore.ieee.org/abstract/document/9138292/}{\nolinkurl{URL}}

\item Chuprov, S.,  Marinenkov, E., Viksnin, I., Reznik, L., \& Khokhlov, I (2020). ``Image Processing in Autonomous Vehicle Model Positioning and Movement Control'' in IEEE 6th World Forum on Internet of Things (WF-IoT) Proceedings, pp. 1-6, doi: 10.1109/WF-IoT48130.2020.9221258. \href{https://ieeexplore.ieee.org/document/9221258}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., Reznik, L., \& Khokhlov, I. (2020). ``Reputation and Trust Models with Data Quality Metrics for Improving Autonomous Vehicles Traffic Security and Safety'' in Proc. IEEE/NDIA/INCOSE Syst. Secur. Symp, pp. 1-8, doi: 10.1109/SSS47320.2020.9174269. \href{https://ieeexplore.ieee.org/document/9174269}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., \& Kim, I. (2019) ``Urban Intersection Management with Connected Infrastructure Objects and Autonomous Vehicles'' in 2019 IEEE International Conference on Connected Vehicles and Expo (ICCVE), pp. 1-4, doi: 10.1109/ICCVE45908.201\\
9.8964917. \href{https://ieeexplore.ieee.org/abstract/document/8964917}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., \& Nedosekin, G. (2019). ``Optimization of Autonomous Vehicles Movement in Urban Intersection Management System'' in 2019 24th Conference of Open Innovations Association (FRUCT), pp. 60-66, doi: 10.23919/FRUCT.2019.8711967. \href{https://ieeexplore.ieee.org/abstract/document/8711967/}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., \& Usova, M. (2019). ``Intersection Management Tasks in Mobile Robotic System with Decentralized Control'' in CEUR Workshop Proceedings, vol. 2344, pp. 1-12. \href{http://ceur-ws.org/Vol-2344/paper7.pdf}{\nolinkurl{URL}}

\item Usova, M., Chuprov, S., Viksnin, I., Gataullin, R., Komarova, A., \& Iuganson, A. (2019). ``Model of Smart Manufacturing System'' in International Symposium on Intelligent and Distributed Computing, pp. 356-362, doi: 10.1007/978-3-030-32258-8\_42. \href{https://link.springer.com/chapter/10.1007/978-3-030-32258-8_42}{\nolinkurl{URL}}

\item Marinenkov, E., Chuprov, S., Viksnin, I., \& Kim, I. (2019). ``Empirical Study on Trust, Reputation, and Game Theory Approach to Secure Communication in a Group of Unmanned Vehicles'' in CEUR Workshop Proceedings, vol. 2590, pp. 1-12. \href{http://ceur-ws.org/Vol-2590/paper28.pdf}{\nolinkurl{URL}}

\item Usova, M., Chuprov, S., Viksnin, I., \& Baranova, O. (2019). ``Model of Secure Informational Messages for Ensuring Informational Interaction in Smart Factory'' in CEUR Workshop Proceedings, vol. 2590, pp. 1-8. \href{http://ceur-ws.org/Vol-2590/short28.pdf}{\nolinkurl{URL}}

\item Viksnin, I., Lyakhovenko, J., Tursukov, N., Chuprov, S., \& Sozinova, E. (2019). ``Empirical Study on Modeling of People Behavior in Emergency'' in CEUR Workshop Proceedings, vol. 2590, pp. 1-8. \href{http://ceur-ws.org/Vol-2590/short33.pdf}{\nolinkurl{URL}}

\item Kim, I., Matos-Carvalho, J. P., Viksnin, I., Campos, L. M., Fonseca, J. M., Mora, A., \& Chuprov, S. (2019). ``Use of Particle Swarm Optimization in Terrain Classification based on UAV Downwash'' in 2019 IEEE Congress on Evolutionary Computation (CEC), pp. 604-610, doi: 10.1109/CEC.2019.8790031. \href{https://ieeexplore.ieee.org/abstract/document/8790031/}{\nolinkurl{URL}}

\item Viksnin, I., Chuprov, S., Usova, M., \& Zakoldaev, D. (2019). ``Police Office Model for Multi-agent Robotic Systems'' in IOP Conference Series: Materials Science and Engineering, vol. 497, no. 1, p. 012036, doi: 10.1088/1757-899X/497/1/012036. \href{https://iopscience.iop.org/article/10.1088/1757-899X/497/1/012036/meta}{\nolinkurl{URL}}

%\textbf{Presented and accepted for publication, will be published soon:}
\end{enumerate}
\end{rSection}

\begin{rSection}{Other Publications and Presentations}
\begin{enumerate}
\itemsep-0.5em

\item Chuprov, S. (2020). ``Intersection Management Tasks Application in Mobile Robotic System with Autonomous Vehicle Models'' in Saint-Petersburg's Government Grant Award Winners, pp. 68-74. \href{https://drive.google.com/file/d/1pG5H6agnzNzFAbElviIHcb7Bj3mRQbco/view?usp=sharing}{\nolinkurl{URL}}

\item Chuprov, S. (2020). ``Reputation, Trust, and Data Quality Concept for Security and Safety Assurance in a Group of Autonomous Vehicles'' in IX Young Scientists Congress Proceedings, Electronic Edition. \href{https://kmu.itmo.ru/digests/article/3817}{\nolinkurl{URL}}

\item Chuprov, S. (2019). ``Security Assurance of Mobile Robotic Systems with Decentralized Control'' in 2019 ITMO University Annotated Master's Research Thesis Proceedings, pp. 66-72. \href{https://drive.google.com/file/d/1N9RQR0rh8hOYZR2xX7PoRvpitzYpxaru/view?usp=sharing}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., \& Kim, I. (2019). ``Organization of Safe Intersections Passage by Unmanned Vehicles in a Mobile Robotic System'' in VIII Young Scientists Congress Proceedings, Electronic Edition. \href{https://kmu.itmo.ru/digests/article/209}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., Kim, I., \& Usova, M. (2019). ``Secure Intersection Management Passage with a Group of Autonomous Vehicles in Mobile Robotic System with Decentralized Control'' in ITMO University Young Scientists Almanac, vol. 2, pp. 43-48. \href{https://research.itmo.ru/file/stat/194/almanah_tom_2_2019_(1).pdf}{\nolinkurl{URL}}

\item Chuprov, S., Viksnin, I., \& Usova, M. (2018). ``Police Office Model with Partial Decentralized Control in Mobile Robotic System'' in Regional Informatics and Information Secutity SPOISU Proceedings, vol. 6, pp. 245-249. \href{http://spoisu.ru/files/riib/riib_6_2018.pdf}{\nolinkurl{URL}}
\end{enumerate}

\textbf{Presentations, forums, workshops, and seminars without publications:}
\begin{enumerate}
\itemsep-0.5em

\item Chuprov, S. (2022). ``Discovering and Addressing Privacy and Robustness Flaws in Federated Learning'' at the Research Idea Ring (RIR) in Computer Science, 17 November 2022, Rochester Institute of Technology, Rochester, NY, USA.

\item Chuprov, S., \& Reznik, L. (2021). ``Reputation and Trust Models with Data Quality Metrics for Improving Autonomous Vehicles Traffic Security and Safety'' at Great Lakes Security Day (GLSD) 2021 Online, 12 November 2021, Rochester, NY, USA. -- \textit{Poster session.}

\item Chuprov, S. (2020). ``Security and Safety Approaches to “Soft” Attacks Detection in Intelligent Systems and IoT'' at Technology Development Trend of Intelligent Internet online workshop, 4 December 2020, Saint-Petersburg, Russia.  

\item Chuprov, S. (2020). ``Reputation and Trust Approach for Cyber-physical Systems Security and Safety Assurance'' at ITMO University's XLIX Research, Educational and Methodical Conference, 29 January 2020 - 1 Febeuary 2020. Saint-Petersburg, Russia. 

\item Chuprov, S. (2019). ``Secure and Optimal Intersections' Traversal by a Group of Autonomous Vehicles in Mobile Robotic System'' at Saint-Petersburg's Academic and Industrial Institutions Students' Grant Award Winners Round Table Discussion ``Natural and Exact Sciences'', 6th December 2019. Saint-Petersburg, Russia.    

\item Chuprov, S. (2019). ``Reputation and Trust-based Approach for Security and Safety Assurance in a Group of Autonomous Vehicles'' at Huawei Trust Worthy Software Technology Forum, 28 - 29 November 2019. Saint-Petersburg, Russia. 

\item Chuprov, S. (2019). ``Multi-Agent Physical Testbed for Smart City's Control and Security Algorithms Verification'' at Geek Picnic, 11 - 12 July 2019. Saint-Petersburg, Russia.

\item Chuprov, S. (2018). ``Multi-agent Systems Laboratory Current Research Projects'' at Saint-Petersburg's International Youth Forum 6.0, 1 December 2018. Saint-Petersburg, Russia. 
\end{enumerate}
\end{rSection}