\documentclass[10pt]{resume} % Use the custom resume.cls style
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{caption}
%\usepackage{xurl}
\usepackage{breakurl}
\usepackage[colorlinks]{hyperref}
\usepackage{comment}
\usepackage[left=0.3in,top=0.3in,right=0.3in,bottom=0.3in]{geometry}
%\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\cv{\url{https://people.rit.edu/sc1723}}
\cvs{\href{https://scholar.google.com/citations?hl=en&authuser=1&user=IpuSnGwAAAAJ}{Google Scholar}~~~~~
\href{https://www.linkedin.com/in/sergei-chuprov-889053174/}{LinkedIn}
}

\name{Sergei Chuprov}
% Your name
\address{PhD Student in Computing and Information Sciences}
\address{Rochester Institute of Technology, Rochester, NY}
% Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\textbf{Email:} sc1723@rit.edu} % Your phone number and email

\begin{document}
\vspace{-0.5cm}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%%%
\begin{comment}
\begin{rSection}{Manifesto}

I am a Ph.D. student in Computer and Information Sciences at the Department of Computer Science at Rochester Institute of Technology. My current research is focused on a security assurance in distributed and multi-agent systems, and ML- and AI-based systems security. 

My comprehensive academic background and valuable research expertise are evidenced by numerous publications and grant awards (please, see below). In 2021, I was awarded the Scholarship of the Russian Federation President for Students Studying Abroad. This Scholarship is designated to encourage students with excellent academic and research achievements for advanced research and cultural exchange experience. I underwent through multiple candidacy selection filters on various levels, from the University to a Russian Federation-wide. My achievements, gained through hard work and with the help of sincere enthusiasm, facilitated to the selection of my candidacy from thousands of others to award the Scholarship. This Scholarship was essential for me, especially in my first PhD year in the US. It helped me to cover my living expenses, which became really high in the end of 2021 due to various economical factors. This financial aid has helped me to focus on my research and academic goals, and to produce numerous research results that will contribute to my PhD thesis. These results include provisional patent application (see Patents section) submitted in August 2022. I highly appreciate the chance to use this Scholarship for the benefit of both myself and the research community.  

% My research is important for industry, and Russian Government made wrong decision. I hope META needs this better.  

Unfortunately, due to the current circumstances occurred in the World since February 2022, The Ministry of Higher Education of the Russian Federation has canceled all the Scholarship award payments to the students studying abroad in the countries, recognized by the Russian Government as ``unfriendly'' on the official level (\href{https://en.wikipedia.org/wiki/Unfriendly_Countries_List}{\nolinkurl{URL}}). I want to express my strongest disapproval with this decision and feel deep misunderstanding. I strongly believe that my research can be beneficial for the industry by making distributed systems more robust, secure, and reliable. I think the Russian Government made the wrongest possible decision by arbitrarily withdraw the intentions to support my research by the reason I chose the ``unfriendly'' country. I believe that Meta's products, services, and end-users will definitely benefit from utilizing my research results. This fellowship will be extremely helpful for me too, as it will give me a chance to gain industry-leading experience and to utilize it in order to pursue my research and academic goals.          
\end{rSection}
\end{comment}

\begin{rSection}{Education}
PhD in Computing and Information Sciences (\textit{expected graduation: Spring-Summer 2024}) \\
{\bf Rochester Institute of Technology, NY, USA} \hfill \small{\em August 2021 - Present}\normalsize\\ 
Golisano College of Computing and Information Sciences\hfill \small\textbf{GPA:} 3.83/4.0 (current)\normalsize\\
\begin{comment}
\textbf{Courses completed:}
\scriptsize
\begin{enumerate}
\itemsep-0.8em 
    \item Research Foundations
    \item Quantitative Foundations
    \item Cyberinfrastructure Foundations
    \item Deep Learning
    \item Research Methods in HCI
    \item Systems \& SCADA Security
    \item Foundations of Intelligent Security Systems
    \item Information Security Risk Management
    \item Colloquium on Computational \& Information Sciences
\end{enumerate}
\normalsize
\end{comment}
%PhD in Information Security (in progress) \\
%{\bf Saint-Petersburg National Research University of} \hfill {\em September 2019 - Present}\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \textbf{GPA:} 4.0/4.0 \small(current)\normalsize\\
%Faculty of Secure Information Technologies\\
\begin{comment}
\textbf{Courses completed:}
\scriptsize
\begin{enumerate}
\itemsep-0.8em 
    \item English Language
    \item Philosophy and History of Science
    \item Psychology and Teaching in Higher Education
    \item Theory and Methodology in Scientific Research
    \item Patents and Intellectual Property Assurance
    \item Modern Methods in Complex Systems Research  
    \item Teaching Practice
    \item Academic Research
\end{enumerate}
\normalsize
\end{comment}
%PhD in Computer Science (in progress) \\
%{\bf Saint-Petersburg National Research University of} \hfill {\em September 2019 - Present}\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \textbf{GPA:} 4.0/4.0 (current)\\
%Faculty of Secure Information Technologies\\

\vspace{-0.3cm}
Master's in Information Security \\
{\bf Saint-Petersburg National Research University of} \hfill \small{\em September 2017 - June 2019}\normalsize\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \small\textbf{GPA:} 4.0/4.0 (with honors)\normalsize   
\\ Faculty of Secure Information Technologies\\
\textbf{Thesis:} Assurance of Information in a Mobile Robotic System with Decentralized Control\\
\begin{comment}
\textbf{Courses completed:}
\scriptsize
\begin{enumerate}
\itemsep-0.8em 
\item Information Security Basics
\item Information Security Management
\item Organizational and Legal Mechanisms for Information Security Assurance
\item Foreign Language in Professional Activity (English)
\item Emotional Regulation Status in Professional Activity
\item Work Practice, Research Work
\item Information Security Risks Management
\item Organization of Information Security Service
\item Mathematical Modeling of Objects and Systems
\item Project Management
\item Information Security Technology
\item Technical Means against Industrial Spying
\item Software and Hardware Information Security Means
\item Cryptosystems Modeling
\item Comprehensive Approach to Information Security Assurance
\end{enumerate}
\normalsize
\end{comment}

%$~$\\
\vspace{-0.3cm}
Bachelor's in Information Security \\
{\bf Saint-Petersburg National Research University of} \hfill \small{\em September 2013 - June 2017}\normalsize\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \small\textbf{GPA:} 3.5/4.0 \normalsize
\\ Faculty of Secure Information Technologies\\
\textbf{Thesis:} Vulnerability Analysis and Classification in Local Networks Based on Microsoft OS Family\\
\begin{comment}
\textbf{Courses completed:}
\scriptsize
\begin{enumerate}
\itemsep-0.8em 
    \item History
    \item Philosophy 
    \item Foreign Language (English)
    \item Economics
    \item Law
    \item Fundamentals of Management Activity
    \item Mathematics
    \item Probability Theory and Mathematical Statistics
    \item Physics
    \item Computer Science
    \item Information Theory
    \item Fundamentals of Information Security
    \item Computer Hardware
    \item Programming Languages
    \item Technology and Methods of Programming
    \item Fundamentals of Electrical Engineering
    \item Electronics and Circuit Design
    \item Data Transmission Networks and Systems
    \item Records Management
    \item Software and Hardware Tools of Information Protection
    \item Technical Information Protection
    \item Cryptographic Methods of Information Protection
    \item Information Technology
    \item Organisational and Legal Support of Information Security
    \item Information Security Management
    \item Health and Safety
    \item Cultural Studies
    \item Social and Political Issues of Modern Society
    \item Ecology
    \item Discrete Mathematics
    \item Advanced Branches of Physics
    \item Concepts of Modern Natural Science
    \item Wave Processes in Media
    \item History and Modern Information Protection System in Russia
    \item Theory of Information Security and Methodology of Information Protection
    \item Information Protection Economics
    \item Information Security Service Organisation and Management
    \item Information Protection Systems in Leading Foreign Countries
    \item Complex Information Protection Systems
    \item Technology of Certification of Information Protection Tools
    \item Information Protection in Database-Management Systems
    \item Protection of Information Processes in Computer Systems
    \item Technology of Vulnerability Detection in Corporate Networks
    \item Protection of Personal Data Processing Systems
    \item Network Operation Systems
    \item Rhetoric
    \item Specialist's Reputation and Corporate Culture
    \item System Theory and System Analysis
    \item Optimization Methods
    \item Graph Theory
    \item Information Protection on the Internet
    \item Modeling of Information Protection Systems 
    \item Information Security Tools Programming
    \item Physical and Wellness Education 
    \item Physical and Wellness Education (Elective course) 
    \item Academic Practical Training (practical training for acquiring basic professional skills and knowledge)
    \item Industrial Placement (practical training for acquiring basic professional skills and experience) including pre-graduation practical training (for execution of graduate qualifying paper)
\end{enumerate}
\normalsize
\end{comment}

\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Academic Work and Teaching Experience}

\begin{comment}  
\textbf{B. Thomas Golisano College of Computer Science, RIT}\\
\textbf{Rochester, NY, USA}\hfill\small{\em September 2022 - present}\normalsize\\
{\em Teaching Assistant (part-time)}
\\\textbf{Scope:} Computing and Information Sciences
\\\textbf{Responsibilities:} Assisting with the teaching activities and grading practical assignments of graduate and undergraduate students. Courses:
\begin{itemize}
\itemsep -0.5em 
    \item CSCI-735 Foundations of Intelligent Security Systems. Instructor: Dr. Leon Reznik.
    \item CSCI-636/536 Information Retrieval. Instructor: Dr. Richard Zanibbi.
\end{itemize}
\end{comment}

\textbf{B. Thomas Golisano College of Computer Science, RIT}\\
\textbf{Rochester, NY, USA}\hfill\small{\em August 2021 - present}\normalsize\\
{\em Graduate Research Assistant (part-time)}
\\\textbf{Scope:} research in the area of Artificial Intelligence- and Machine Learning-based systems security, Data Quality and security assurance, robustness of Machine Learning-end systems with integrated network facilities. 
\\\textbf{Results:} 2 patent applications; more than 10 published papers in refereed journals and conference proceedings (please, see Publication List below). 

\textbf{Mobile Intelligent Systems Laboratory, ETU ``LETI'' University}
\\
\textbf{Saint Petersburg, Russia}\hfill \small{\em May 2021 - August 2021}\normalsize\\
{\em Researcher (part-time remote position)}
\\\textbf{Scope:} research in the area of Cyber-Physical Systems security and safety, Intelligent Systems security. 
\\\textbf{Results:} developed models and software tools for Reputation and Trust-based simulation environment to model communication in decentralized IoT networks; developed projects' reports and technical documentation; 7 published papers in refereed journals and conference proceedings (please, see Publication List below).     

%\begin{itemize}
%\itemsep-0.5em 
%    \item \textbf{Teamwork:} the laboratory consists of undergraduate, graduate and postgraduate students.
%\end{itemize}

%\begin{itemize}
%\itemsep-0.5em 
%    \item \textbf{Teamwork:} the laboratory consists of undergraduate, graduate and postgraduate students.
%    \item \textbf{Leadership:} leading a team of 4-6 participants, guiding students in undergraduate studies.
%\end{itemize}

\textbf{Department of Secure Information Technologies, ITMO University}\\
\textbf{Saint Petersburg, Russia}\hfill\small{\em September 2019 - May 2021}\normalsize\\
{\em Teaching Assistant (part-time)}
\\\textbf{Scope:} undergraduate and graduate courses teaching in the area of Information Security.
\\\textbf{Results:} gained experience in teaching laboratory and practical sessions for the classes of 10-20 undergraduate and graduate students; developed coursework for the "Functional Security and Safety Assurance in Unmanned Vehicles" Master's degree program, established at ITMO in 2019. 

\textbf{Department of Secure Information Technologies, ITMO University}\\
\textbf{Saint Petersburg, Russia}\hfill\small{\em May 2018 - May 2021}\normalsize
\\{\em Researcher (part-time)}
\\\textbf{Scope:} research in the area of Information Security, multi-agent mobile robotic systems security, knowledge representation in intelligent systems.
\\\textbf{Results:} developed security and safety models and methods for decentralized and multi-agent mobile robotic systems (please, see Projects below); developed security-inspired smart factory models in AnyLogic simulation environment; 14 publications in refereed journals and conference proceedings (please, see Publication List below).        
\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------

%\begin{rSection}{Non-academic Work Experience}

%\textbf{OOO Coffee Sirena (Starbucks), Saint-Petersburg}\hfill{\em July 2013 - May 2018}\\{\em Assistant Store Manager (part-time)}
%\\\textbf{Scope:} Catering
%\\\textbf{Job responsibilities:} Responsibility for the economic performance of a coffee shop, staff recruitment and training, leadership of a team of 6-10 persons, resource allocation.
%\\\textbf{Website:} \url{http://www.starbucks.ru/}
%\end{rSection}

\begin{rSection}{Projects}

{\bf Enhancing Security and Privacy of the Conventional Federated Learning Architecture} (participant) \\
\hspace*{\fill} {\em September 2022 - Present}
\vspace{-0.3cm}
\begin{itemize}
\itemsep-0.5em 
\item \textbf{Results:} 1 filed patent application; 1 paper submission in-progress. 
\item The project is supported by the United States Military Academy (USMA) and is accomplished under Grant Number W911NF-20-1-0337. 
\end{itemize}

{\bf Developing Methods and Tools for Machine Learning Robustness Assurance under Vulnerable Cyberinfrastructure and Varying Data Quality} (participant) \hspace*{\fill} {\em May 2022 - Present}
\vspace{-0.4cm}
\begin{itemize}
\itemsep-0.5em 
\item \textbf{Results:} 1 filed patent application; 4 published papers.
%The objective of this project is to develop methods and tools for enhancing ML Robustness, which will allow to significantly improve security and safety of ML systems integrated with network facilities and other modern computing and cyberinfrastructure. 
%In contrast to other approaches, we consider MLINs from the system integration perspective, and propose methods that tide MLIN components together into an interrelated structure with the goal to improve its Robustness to potential data integrity violations. 
\item The project is supported by a grant from the U.S. Civilian Research \& Development Foundation (CRDF Global) with funding from the United States Department of State. 
\end{itemize}

{\bf Enhancing Sensor Network Security with Reputation and Trust-Based Technique} (participant)\\ \hspace*{\fill} {\em September 2022 - January 2023}
\vspace{-0.2cm}
\begin{itemize}
\itemsep-0.8em 
\item \textbf{Results:} developed software simulation environment that allows modeling the communication between sensors and malicious attacks against the quality of communicated data. At present, the developed software methods and tools undergo intellectual property registration procedures.   
\end{itemize}

{\bf Development of Hardware and Software Modules for Critical Objects Monitoring over the Conditions of Uncertainty and Data Incompleteness for Malicious Attacks Prevention and Mitigation} (participant) \hspace*{\fill} {\em September 2019 - October 2020}
\vspace{-0.2cm}
\begin{itemize}
\itemsep-0.5em
\item \textbf{Results:} developed documentation, and software and hardware prototypes, implemented by Murmansk Commercial Seaport OAO, Murmansk, Russia.  
\item The work was financially supported by the Ministry of Science and Higher Education of the Russian Federation under the agreement \href{https://fcpir.ru/participation_in_program/contracts/05.605.21.0189/}{\nolinkurl{No. 05.605.21.0189}}. 
\end{itemize}

{\bf Development of a Quantum Secure Hybrid Platform for Distributed Cyber-Physical Systems Control} (participant) \hspace*{\fill} {\em May 2018 - August 2019}
\begin{itemize}
\itemsep-0.5em
\item \textbf{Results:} developed documentation and software and hardware prototypes, implemented at ITMO University for further research and educational purposes.
\item The work was financially supported by the Government of Russian Federation, Grant 074-U01.
\end{itemize}

{\bf Development of Experimental Testbed for Smart City Control and Security Algorithms Research and Verification} (participant) \hfill \hfill {\em May 2018 - March 2019}
\begin{itemize}
\itemsep-0.5em
\item \textbf{Results:} developed documentation, physical testbed, and 10 autonomous vehicle models; 3 published papers. 
\item A video of the developed testbed can be found in a public access: \href{https://vk.com/video-175152723_456239017}{\nolinkurl{URL}}.
\end{itemize}
\end{rSection}


\begin{comment}
\begin{rSection}{Educational Projects}
\textbf{Development of a cryptosystem model for asymmetric encryption}
\\%A small project on the course of Cryptosystem Modeling.
A model of a cryptosystem on the Python language was developed, allowing to perform secure data transmission with session key and using AES and RSA algorithms.


\textbf{Development of an integrated information security system for an enterprise}
\\A model of an integrated information security system was developed in accordance with the standards and requirements adopted in the Russian Federation.


\textbf{Development of an economically feasible information protection system for an enterprise}
\\An assessment of the damage caused by the realization of possible threats to information security was carried out, a risk assessment was conducted and the appropriateness of the proposed information protection tools was evaluated.
\end{rSection}
\end{comment}



%\begin{rSection}{Other projects}


%\end{rSection}

\begin{rSection}{Grants and awards}

\textbf{NSF grant that covers participation in POWDER-RENEW Mobile and Wireless Week 2023} \\
Salt Lake City, UT, USA \hfill {\em January 2023}

\textbf{Amazon AWS Cloud Credit for Research} \\ \textbf{Awarded an AWS research promotional credit for one year} \\
Rochester, NY, USA \hfill {\em August 2022}

\textbf{Saint-Petersburg’s Academic and Industrial Institutions Students’ Grant} \\ \textbf{Award for 2022 Academic Year} \\
Saint-Petersburg, Russia \hfill {\em July 2022} 

\textbf{IEEE INFOCOM 2022 Student Conference Grant}\\
London, UK \hfill {\em May 2022}

\textbf{Rochester Institute of Technology PhD Research and Tuition Scholarship} \\
Rochester, NY, USA \hfill {\em August 2021}

\textbf{Scholarship of the Russian Federation President for Students of Higher Education} \\ \textbf{Universities Studying Abroad in 2021/2022 Academic Year} \\
Saint-Petersburg, Russia \hfill {\em May 2021}

\textbf{Scholarship of the Russian Federation President and Government for the} \\ \textbf{Students of Priority Education Directions in 2021/2022 Academic Year} \\
Saint-Petersburg, Russia \hfill {\em May 2021}

\textbf{Scholarship of the Russian Federation President and Government for the}\\ \textbf{Students of Priority Education Directions in 2020/2021 Academic Year} \\
Saint-Petersburg, Russia  \hfill {\em May 2020} 

\textbf{Saint-Petersburg's Academic and Industrial Institutions Students' Grant Award} \\
Saint-Petersburg, Russia \hfill {\em October 2019}

\textbf{ITMO University's Best Student's Research Master Thesis Award} \\
Saint-Petersburg, Russia \hfill {\em August 2019}

\textbf{Scholarship of the Russian Federation Government} \\
Saint-Petersburg, Russia \hfill {\em September 2019}
\end{rSection}

\begin{rSection}{Additional Research Experience}
Summer research program in Cybersecurity under the supervision of Prof. Leon Reznik\\
{\bf Rochester Institute of Technology} \hfill {\em June 2019 - August 2019}\\ \textbf{B. Thomas Golisano College of Computing and Information Sciences}\\
\textbf{Scope:} Security and Safety Assurance in a Group of Autonomous Vehicles with Reputation, Trust, and Data Quality Approach.\\
\textbf{Results:} 3 published papers.
\end{rSection}

\begin{comment}
\begin{rSection}{Special Education in English}
{\bf Alpha-Dialogue Intensive Language Session, Pargas, Finland} \hfill {\em 3-12th January 2013}
\\ Intensive English language course. Became the winner of the program for the best progress in the English language in my age category.


{\bf Embassy English Language School, Hastings, UK} \hfill {\em 25th March - 7th April 2012}
\\ Intensive English course during spring school holidays. At the end of the course, received a certificate of B2 level and positive feedback from teachers.

{\bf EF International Language School, Dublin, Ireland} \hfill {\em 4-22th July 2011}
\\ Successfully completed a full-time coourse at EF Summer School of English Language. Received a certificate of A2 level.
\end{rSection}
\end{comment}

\begin{rSection}{Advanced Training Courses}
Online intensive course: ``Blended Learning: Digital Teacher Competencies''\\
{\bf Saint-Petersburg National Research University of} \hfill {\em 24 - 29 August 2020}\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \\
72 hours of online intensive lectures, practice, and master-classes with a final project defending. Confirmed by a state-recognized certificate.

``Foundations of Public Speaking in the 21st Century''\\
{\bf Saint-Petersburg National Research University of} \hfill {\em 13th March - 24th April 2019}\\ \textbf{Information Technologies, Mechanics and Optics, Russia} \hfill \\
72 hours of intensive lectures, practice, and master-classes with final public-speaking project defending. Confirmed by a state-recognized certificate.
\end{rSection}

\begin{rSection}{Tools}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Modeling and Analysis \ & Matlab, AnyLogic, Python (NumPy, pandas, scikit-learn, etc), IBM SPSS,\\ & Network Simulator (2,3), Simulator of Urban Mobility (SUMO), CARLA \\
Software Development & Python, C/C++, Git \\
Technical Writing & \LaTeX, MS Office 
%Languages \ & English, Russian (native) \\
\end{tabular}
\end{rSection}

\begin{rSection}{Other}

\textbf{Related publications in social media:}
\item ITMO’s R\&D Project Results and Their Applications: \href{https://news.itmo.ru/en/science/cyberphysics/news/9255/#:~:text=100%25%20of%20attacks.%E2%80%9D-,A%20drone%20model%20testing%20stand,-Sergey%20Chuprov%E2%80%99s}{\nolinkurl{URL}}

\end{rSection}

\input{publications}


%%%
\begin{comment}
\begin{rSection}{Summary}
Second-year PhD student in Computer Science. Interesting in Cyber-physical systems and Smart City applications security and safety research, working on the doctoral thesis: Models and Methods for Security and Safety Assurance in Distributed Mobile Robotic Systems.  
I want to advance my research career through international cooperation and PhD study in Computer Science/Cybersecurity.  
\end{rSection}
\end{comment}

%\begin{rSection}{Personal Traits}
%\item Great time and project management skills. Like to allocate time in a manner to always keep up. 
%\item Strong teamwork \& collaboration skills. Able to work as an individual as well as in group.
%\item Ability to build relationships and quickly adapt to a new team.
%\item Fast learner. Like to analyze and penetrate the essence of the processes.
%\end{rSection}
\end{document}
